### 2023-11-22 texts/paper_closing.tex
add summary statistics table, also update tasks

% Created 2023-11-21 di 10:37
% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{article}

@@

@@

% latex table generated in R 4.3.2 by xtable 1.8-4 package
% Tue Nov 21 10:36:10 2023
\begin{table}[ht]
\centering
\begin{tabular}{p{0mm}lD{)}{)}{8)3}}
  \hline 
 \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{r\_more}\\ 
 \hline
  \multicolumn{3}{l}{\textbf{Founder}} \\ 
 & Gender - Female & .31 \; (0.36) \\ 
   & Gender - Couple & -.07 \; (0.36) \\ 
   & Founder died & .11 \; (0.51) \\ 
   \multicolumn{3}{l}{\textbf{Museum}} \\ 
 & Self-Identification - Foundation & .76 \; (0.46) \\ 
   & Self-Identification - Collection & .52 \; (0.54) \\ 
   & Self-Identification - Other & 1.12 \; (0.36)^{**} \\ 
   & Founder name in Museum name & -.27 \; (0.31) \\ 
   & MOW inclusion & -.97 \; (0.40)^{*} \\ 
   \multicolumn{3}{l}{\textbf{Environment}} \\ 
 & PM density & -.03 \; (0.03) \\ 
   & PM density$^{2}$ & .00 \; (0.00) \\ 
   \hline
 & Museum-years & 7282 \\ 
   & Closures & 53 \\ 
   & log. Likelihood & -271.10 \\ 
   & AIC & 562.20 \\ 
   & BIC & 581.91 \\ 
   \hline 
 \multicolumn{3}{l}{\footnotesize{standard errors in parantheses.\textsuperscript{***}p $<$ 0.001;\textsuperscript{**}p $<$ 0.01;\textsuperscript{*}p $<$ 0.05.}}
\end{tabular}
\caption{Cox Proportional Hazards Regression Results} 
\label{tbl:t_reg_coxph}
\end{table}

@@

% latex table generated in R 4.3.2 by xtable 1.8-4 package
% Tue Nov 21 10:36:04 2023
\begin{table}[ht]
\centering
\begin{tabular}{p{0mm}lD{.}{.}{5}D{.}{.}{5}D{.}{.}{5}}
  \hline 
 \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{Kaplan-Meier} & \multicolumn{1}{l}{Identity} & \multicolumn{1}{l}{Rank}\\ 
 \hline
  \multicolumn{2}{l}{\textbf{Founder}} \\ 
 & Founder died & .68 & .64 & .87 \\ 
   & Gender - Couple & .35 & .26 & .35 \\ 
   & Gender - Female & .67 & .73 & .60 \\ 
   \multicolumn{2}{l}{\textbf{Museum}} \\ 
 & Founder name in Museum name & .06 & .05 & .05^{*} \\ 
   & MOW inclusion & .39 & .43 & .59 \\ 
   & Self-Identification - Collection & .72 & .64 & .44 \\ 
   & Self-Identification - Foundation & .78 & .90 & .73 \\ 
   & Self-Identification - Other & .76 & .79 & .63 \\ 
   \multicolumn{2}{l}{\textbf{Environment}} \\ 
 & PM density & .78 & .80 & .81 \\ 
   & PM density$^{2}$ & .93 & .89 & .87 \\ 
   \multicolumn{2}{l}{\textbf{Miscellaneous}} \\ 
 & Global & .41 & .32 & .41 \\ 
   \hline 
 \multicolumn{3}{l}{\footnotesize{\textsuperscript{***}p $<$ 0.001;\textsuperscript{**}p $<$ 0.01;\textsuperscript{*}p $<$ 0.05.}}
\end{tabular}
\caption{Z-test of proportional hazards} 
\label{tbl:t_coxzph}
\end{table}

>>>>

% Created 2023-11-22 wo 17:48
% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{article}

@@

% latex table generated in R 4.3.2 by xtable 1.8-4 package
% Wed Nov 22 17:48:02 2023
\begin{table}[ht]
\centering
\begin{tabular}{llrrrrrr}
  \hline
 & & \multicolumn{2}{c}{Museum} & \multicolumn{4}{c}{Museum-year} \\ 
\cmidrule(r){3-4}\cmidrule(r){5-8} \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{Count} & \multicolumn{1}{l}{Mean} & \multicolumn{1}{l}{Mean} & \multicolumn{1}{l}{SD} & \multicolumn{1}{l}{Min.} & \multicolumn{1}{l}{Max.}\\ 
 \hline
  \multicolumn{8}{l}{\textbf{Founder}} \\ 
 & Gender - Male & 275 & 0.574 &  0.589 &  0.49 & 0 &  1 \\ 
   & Gender - Female & 76 & 0.159 &  0.162 &  0.37 & 0 &  1 \\ 
   & Gender - Couple & 128 & 0.267 &  0.249 &  0.43 & 0 &  1 \\ 
   & Founder died & 58 & 0.121 &  0.097 &  0.30 & 0 &  1 \\ 
   \multicolumn{8}{l}{\textbf{Museum}} \\ 
 & Self-Identification - Museum & 179 & 0.374 &  0.417 &  0.49 & 0 &  1 \\ 
   & Self-Identification - Foundation & 101 & 0.211 &  0.188 &  0.39 & 0 &  1 \\ 
   & Self-Identification - Collection & 74 & 0.154 &  0.135 &  0.34 & 0 &  1 \\ 
   & Self-Identification - Other & 125 & 0.261 &  0.259 &  0.44 & 0 &  1 \\ 
   & Founder name in Museum name & 229 & 0.478 &  0.491 &  0.50 & 0 &  1 \\ 
   & MOW inclusion & 91 & 0.190 &  0.317 &  0.47 & 0 &  1 \\ 
   \multicolumn{8}{l}{\textbf{Environment}} \\ 
 & PM density &  &  & 19.615 & 18.32 & 1 & 62 \\ 
   & Europe and North America & 313 & 0.653 &  0.651 &  0.48 & 0 &  1 \\ 
   & Region - Africa & 7 & 0.015 &  0.013 &  0.11 & 0 &  1 \\ 
   & Region - Asia & 127 & 0.265 &  0.278 &  0.45 & 0 &  1 \\ 
   & Region - Europe & 242 & 0.505 &  0.500 &  0.50 & 0 &  1 \\ 
   & Region - Latin America & 22 & 0.046 &  0.040 &  0.20 & 0 &  1 \\ 
   & Region - North America & 71 & 0.148 &  0.150 &  0.36 & 0 &  1 \\ 
   & Region - Oceania & 10 & 0.021 &  0.018 &  0.13 & 0 &  1 \\ 
   \hline
\end{tabular}
\caption{Summary Statistics} 
\label{tbl:t_sumstats}
\end{table}

@@

% latex table generated in R 4.3.2 by xtable 1.8-4 package
% Wed Nov 22 17:42:15 2023
\begin{table}[ht]
\centering
\begin{tabular}{p{0mm}lD{)}{)}{8)3}}
  \hline 
 \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{r\_more}\\ 
 \hline
  \multicolumn{3}{l}{\textbf{Founder}} \\ 
 & Gender - Female & .31 \; (0.36) \\ 
   & Gender - Couple & -.07 \; (0.36) \\ 
   & Founder died & .11 \; (0.51) \\ 
   \multicolumn{3}{l}{\textbf{Museum}} \\ 
 & Self-Identification - Foundation & .76 \; (0.46) \\ 
   & Self-Identification - Collection & .52 \; (0.54) \\ 
   & Self-Identification - Other & 1.12 \; (0.36)^{**} \\ 
   & Founder name in Museum name & -.27 \; (0.31) \\ 
   & MOW inclusion & -.97 \; (0.40)^{*} \\ 
   \multicolumn{3}{l}{\textbf{Environment}} \\ 
 & PM density & -.03 \; (0.03) \\ 
   & PM density$^{2}$ & .00 \; (0.00) \\ 
   \hline
 & Museum-years & 7282 \\ 
   & Closures & 53 \\ 
   & log. Likelihood & -271.10 \\ 
   & AIC & 562.20 \\ 
   & BIC & 581.91 \\ 
   \hline 
 \multicolumn{3}{l}{\footnotesize{standard errors in parantheses.\textsuperscript{***}p $<$ 0.001;\textsuperscript{**}p $<$ 0.01;\textsuperscript{*}p $<$ 0.05.}}
\end{tabular}
\caption{Cox Proportional Hazards Regression Results} 
\label{tbl:t_reg_coxph}
\end{table}

@@

% latex table generated in R 4.3.2 by xtable 1.8-4 package
% Wed Nov 22 17:42:09 2023
\begin{table}[ht]
\centering
\begin{tabular}{p{0mm}lD{.}{.}{5}D{.}{.}{5}D{.}{.}{5}}
  \hline 
 \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{Kaplan-Meier} & \multicolumn{1}{l}{Identity} & \multicolumn{1}{l}{Rank}\\ 
 \hline
  \multicolumn{2}{l}{\textbf{Founder}} \\ 
 & Founder died & .68 & .64 & .87 \\ 
   & Gender - Couple & .35 & .26 & .35 \\ 
   & Gender - Female & .67 & .73 & .60 \\ 
   \multicolumn{2}{l}{\textbf{Museum}} \\ 
 & Founder name in Museum name & .06 & .05 & .05^{*} \\ 
   & MOW inclusion & .39 & .43 & .59 \\ 
   & Self-Identification - Collection & .72 & .64 & .44 \\ 
   & Self-Identification - Foundation & .78 & .90 & .73 \\ 
   & Self-Identification - Other & .76 & .79 & .63 \\ 
   \multicolumn{2}{l}{\textbf{Environment}} \\ 
 & PM density & .78 & .80 & .81 \\ 
   & PM density$^{2}$ & .93 & .89 & .87 \\ 
   \multicolumn{2}{l}{\textbf{Miscellaneous}} \\ 
 & Global & .41 & .32 & .41 \\ 
   \hline 
 \multicolumn{3}{l}{\footnotesize{\textsuperscript{***}p $<$ 0.001;\textsuperscript{**}p $<$ 0.01;\textsuperscript{*}p $<$ 0.05.}}
\end{tabular}
\caption{Z-test of proportional hazards} 
\label{tbl:t_coxzph}
\end{table}
